Embodied Neuromorphic Benchmarks

### 2015-08-16 paper/paper.tex
Added circles to figure for clarity

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/fig_ev3}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:ev3} Figure \arabic{figure}.}{ Adaptive control of the EV3 lego robot used for calibrating the minimal simulation.
 The effects of adaptation over two different desired trajectories are shown.  Without adaptation, the joints $q$ do not reach the desired $q_d$ when $q_d$ is large (which
 is when the external force is largest).  With adaptation, $q$ is closer to $q_d$ after about 5 seconds, showing that the system has quickly learned to compensate.}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/fig_ev3}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:ev3} Figure \arabic{figure}.}{ Adaptive control of the EV3 lego robot used for calibrating the minimal simulation.
 The effects of adaptation over two different desired trajectories are shown.  Without adaptation, the joints $q$ do not reach the desired $q_d$ when $q_d$ is large (which
 is when the external force is largest).  With adaptation, $q$ is closer to $q_d$ after about 5 seconds, showing that the system has quickly learned to compensate.
 Points in time where the improvement is clearest are circled.}
\end{figure}
